Untitled

### 2024-10-30 code/manuscript_altanalysis.Rmd
finalize tables and figures

```{r}
library(readxl)
library(did2s)
library(did)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
library(ivreg)
library(fixest)
library(sandwich)
library(lmtest)
```

@@

included.years <- 2010:2023
included.treat <- 2013:2023

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  #filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2023`) %>% 
  pivot_longer(cols = c(`2010`:`2023`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  #filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc %>% filter(ID.x == "90")
```

@@

df.mt <- dfc %>% 
  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, log(Total / Staff))) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
  mutate(dm.rate = dm.rate * 100, 
         htn.rate = htn.rate * 100, 
         pap.rate = pap.rate * 100, 
         crc.rate = crc.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         asthma.rate = asthma.rate * 100, 
         cad.rate = cad.rate * 100, 
         ivd.rate = ivd.rate * 100)

@@

@@

@@

@@

  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`)

@@

core.did.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 4, "Quality of Care" = 6, "Patient Complexity" = 2, "Payer Mix" = 4, "Finances" = 6)) %>% 
  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Incumbent Clinics" = 3))

did2s(
      data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% filter(Year < 2020 ) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0)) %>% filter(!is.na(Urban)), 
      yname = "Staff", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + I(Tx * value),
        cluster_var = "ID",
      verbose = TRUE
    )

df.temptemp %>% 
    ungroup() %>% 
  group_by(Tx) %>% 
  summarise(mean(Qcomp, na.rm = TRUE))

@@

es.direct <- did2s(
  data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) , 
  yname = "Qcomp", 
  treatment = "Tx",
  first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
    second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
    cluster_var = "ID", 
  verbose = TRUE)

cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
      cbind(Group = "Direct",es.direct$coeftable)) %>% 
  data.frame() %>% 
  mutate(estimate = as.numeric(Estimate), 
         std.error = as.numeric(Std..Error), 
         YearRel = as.numeric(YearRel)) %>% 
  filter(abs(YearRel) <= 6) %>% 
 ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

m1coeffs_cl <- coeftest(model, vcov = vcovCL, cluster = ~ID)
m1coeffs_cl

@@

reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
head(summary(reduced)$coeff) %>% as.data.frame()

@@

df.temptemp %>% 
  filter(Year == 2012) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Staff) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  geom_dl(label=c(rep("0 Competitors", length(unique(p$Year))), rep("1 Competitor", length(unique(p$Year))), rep("2 Competitors", length(unique(p$Year))), rep("3+ Competitors", length(unique(p$Year)))), 
          method = list("last.points", hjust = 1, vjust = c(2, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag)

@@

for (k in 1:8){

  df.z.temp2 <- df.z.temp #%>% filter(Att == 0 | Att > 2010)
  colnames(df.z.temp2)[k] <- "Outcome"
  model <-  did2s(
      data = df.z.temp2, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
      #second_stage = ~ i(Tx , ref = FALSE)  + I(Tx * DirectlyTreated),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:8], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, `Pr...t..`, Estimate.1, `95% CI.1`, `Pr...t...1`)

zip.estimates <- zip.estimates[c(1, 6, 2:5, 7:8),]
rownames(zip.estimates) <- NULL

>>>>

```{r}
library(readxl)
library(did2s)
library(did)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
library(tigris)
library(usmap)
library(ivreg)
library(fixest)
library(sandwich)
library(lmtest)
library("viridis")

@@

included.years <- 2009:2023
included.treat <- 2011:2023

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  #filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2023`) %>% 
  pivot_longer(cols = c(`2009`:`2023`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  #filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc %>% filter(ID.x == "90")

@@

df.mt <- dfc %>% 
  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, (Total / Staff))) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
  mutate(dm.rate = dm.rate * 100, 
         htn.rate = htn.rate * 100, 
         pap.rate = pap.rate * 100, 
         crc.rate = crc.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         asthma.rate = asthma.rate * 100, 
         cad.rate = cad.rate * 100, 
         ivd.rate = ivd.rate * 100)

@@

df.temptemp <- df.temptemp %>% 
  left_join(df.temptemp %>% 
  group_by(ID) %>% 
  summarise(n()) %>% 
  filter(`n()` != length(included.years)), by = c("ID")) %>% 
  filter(is.na(`n()`))

possible.vecs <- rep(included.treat, df.temptemp %>% 
  filter(Tx == 1 & Year > 2010) %>% 
  summarise(EarlyTx = min(Year)) %>% 
  select(EarlyTx) %>% 
  unlist() %>% 
  table() )

# 
# df.temptemp <- df.temptemp %>% 
#   left_join(df.temptemp %>% 
#   #filter(Year == 2012) %>% 
#   mutate(Treat = ifelse(Att > 0 & value_last - value_first > 0, "Treated", "Control")) %>% 
#   select(Treat, ID, Tx, Att, value_min, value_max, value_first, value_last) %>% 
#   group_by(Treat, ID, Att, value_min, value_max, value_first, value_last) %>% 
#   summarise(max(Tx, na.rm = TRUE)) %>% 
#   arrange(Att), by = c("ID"))
# #

set.seed(123)
df.temptemp <- df.temptemp %>% 
  #filter(Year == 2012) %>% 
  mutate(Treat = ifelse(Att > 2009 & value_last - value_first > 0, "Treated", "Control")) %>% 
  mutate(Att.random = ifelse(Treat == "Control", sample(possible.vecs, size = 1, replace = T), Att)) %>% 
  mutate(year.rel = Year - Att.random) %>% 
  mutate(Att = ifelse(Att == 2009, 0, Att))

df.temptemp <- df.temptemp #%>% filter(Att %notin% c(2011))

table(df.temptemp$Att)

@@

## Demographics

df.temptemp %>% 
  filter(Year == 2012) %>% 
  mutate(Treat = ifelse(Att > 0 & value_last - value_first > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Staff) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))

df.temptemp %>% 
  filter(Year == 2012) %>% 
  ungroup() %>% 
  mutate(Change = value_last - value_first) %>% 
  select(value_first, Change) %>% 
  table()

## Final Data
demo1 <- df.temptemp %>% 
  filter(year.rel %in% c(-1, 0)) %>% 
  ungroup() %>% 
  mutate(Gx = paste(Treat, year.rel, sep = ": Year Relative ")) %>% 
  select(Gx, Pct.NHA:Pct.Homeless, UrbanRuralFlag) %>% 
  tbl_summary(by = Gx, 
              missing = "no", # don't list missing data separately
      statistic = all_continuous() ~ "{mean} ({sd})",
      digits = all_continuous() ~ c(2,2)
    )

demo2 <- df.temptemp %>% 
  filter(year.rel %in% c(-1, 0)) %>% 
   ungroup() %>% 
  mutate(Gx = paste(Treat, year.rel, sep = ": Year Relative ")) %>% 
  select(year.rel, ID, Treat, Total, Pct.NHA:Pct.Homeless, UrbanRuralFlag) %>% 
  pivot_longer(c(Total:Pct.Homeless)) %>% 
  pivot_wider(id_cols = c(ID, name, Treat), names_from = year.rel, values_from = value) %>% 
  mutate(diff = `0` - `-1`) %>% 
  select(ID, name, Treat, diff) %>% 
  pivot_wider(id_cols = c(ID, Treat), names_from = name, values_from = diff) %>% 
  ungroup() %>% 
  select(Treat, Pct.NHA:Pct.Homeless) %>% 
  tbl_summary(by = Treat, 
              missing = "no", # don't list missing data separately
      statistic = all_continuous() ~ "{mean} ({sd})",
      digits = all_continuous() ~ c(2,2)
    ) %>% 
  add_difference()

tbl_merge(tbls = list(demo1, demo2)) %>%
  modify_spanning_header(everything() ~ NA_character_)

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, color = CompetitorsInArea)) + ylab("FQHCs") + 
  geom_point(size = 1.1) + geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  geom_dl(label=c(rep("0 Rivals", length(unique(p$Year))), rep("1 Rival", length(unique(p$Year))), rep("2 Rivals", length(unique(p$Year))), rep("3+ Rivals", length(unique(p$Year)))), 
          method = list("last.points", hjust = 1, vjust = c(1.5, 2.5, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
  guides(colour = "none") +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

##  Trends over time, figure 1 - black and white for milbank

plot0 <- p %>% 
  arrange(CompetitorsInArea) %>% 
  ggplot(aes(x = Year, y = Count, group = CompetitorsInArea, linetype = CompetitorsInArea)) + ylab("FQHCs") + 
  #geom_point(size = 1.1) + 
  geom_line(size = 1.1) + theme_tufte_revised() + ggtitle("FQHCs by Number of Colocated FQHCs") + 
  #geom_dl(label=c(rep("0 Rivals", length(unique(p$Year))), rep("1 Rival", length(unique(p$Year))), rep("2 Rivals", length(unique(p$Year))), rep("3+ Rivals", length(unique(p$Year)))), 
   #       method = list("last.points", hjust = 1, vjust = c(-3, 2, 2.5, -1), cex = 1.5), inherit.aes=T ) + 
  #guides(linetype = "none") + 
  guides(linetype = guide_legend(title = "# other CHCs\nin Incumbent's\nService Area")) + 
  scale_linetype_manual(values=c(1,2,3, 4)) + 
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))

plot1 <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
            group_by(Zip, Year) %>% 
  summarise(Counts = n()) %>% 
  #summarise(Counts = n_distinct(`Grant Number`)) %>% 
  ungroup() %>% 
  group_by(Year, Counts) %>% 
  summarise(Zips = n()) %>% 
  mutate(Counts.f = as.factor(ifelse(Counts >= 2, "2+", Counts))) %>% 
  group_by(Counts.f, Year) %>% 
  summarise(Zips = sum(Zips)) %>% 
  #filter(Year >= 2010) %>% 
  ggplot(aes(x = Year, y = Zips, group = Counts.f, linetype = Counts.f)) + 
  #geom_point(size = 1.1) + 
  geom_line(size = 1.1) + theme_tufte_revised() + 
  ggtitle("Zip Codes by Number of FQHC Sites") + 
  #geom_dl(label=c(rep("1 Site", length(unique(p$Year))), rep("2+ Sites", length(unique(p$Year)))), method = list("last.points", hjust = 1, vjust = -1, cex = 1.5), inherit.aes=T ) + 
  #guides(linetype = "none") + 
  ylim(0, 4000) +theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold")) + 
  scale_linetype_manual(values=c(5, 6)) + 
  guides(linetype = guide_legend(title = "# CHC Sites by\nZip Code"))

@@

   event_study(data = df.temptemp %>% mutate(ifelse(Att == 2009, 0, Att)),
  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag) %>%
  filter(abs(term) <= 8) %>%
  filter(estimator == "Gardner (2021)") %>%
  #filter(estimator == "Callaway and Sant'Anna (2020)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Outcomes") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

core.did.estimates <- data.frame(cbind(colnames(df.temptemp)[17:38], (coeffs.did[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, Pr...t..)

@@

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp:Staff) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:Staff) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
  cbind(core.did.estimates) %>% 
   select(name, `Control_0`, `Control_1`, `Treated_0`, `Treated_1`, Unadjusted, Estimate, `95% CI`, Pr...t..) %>% 
  mutate(`% Change` = round(Estimate / `Treated_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, Pr...t.., `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","p-value", "% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 4))

@@

# es.direct <- did2s(
#   data = df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) %>% mutate(Mix = Pct.COM * Total / 100) %>% mutate(Urban = ifelse(UrbanRuralFlag == "Urban", 1, 0))  %>% mutate(rel_year = ifelse(Att == 0, Inf, Year - Att)) , 
#   yname = "Complexity", 
#   treatment = "Tx",
#   first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year, 
#     second_stage = ~ i(rel_year, ref = c(-1, Inf)) ,
#     cluster_var = "ID", 
#   verbose = TRUE)
# 
# 
#  
# cbind(YearRel = gsub("rel_year::", "", rownames(es.direct$coeftable)), 
#       cbind(Group = "Direct",es.direct$coeftable)) %>% 
#   data.frame() %>% 
#   mutate(estimate = as.numeric(Estimate), 
#          std.error = as.numeric(Std..Error), 
#          YearRel = as.numeric(YearRel)) %>% 
#   filter(abs(YearRel) <= 6) %>% 
#  ggplot(aes(x = YearRel, y = estimate, color = Group)) + geom_point(position = position_dodge(0.9), size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ #theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) +
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points")
#

@@

m1coeffs_cl <- coeftest(model, vcov = vcovCL, cluster = ~ID)

@@

# reduced <- lm(data = df.temptemptemp, Closed ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag )
# head(summary(reduced)$coeff) %>% as.data.frame()

@@

@@

df.z.temp <- df.z %>% mutate(Tx = ifelse(value - 1 >= 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z >= 2010, 1, 0)) %>% 
  #df.z %>% mutate(Tx = ifelse(value - 1 > 1, 1, value - 1)) %>% filter(!is.na(Tx)) %>% mutate(DirectlyTreated = ifelse(Att.z > 2010, 1, 0)) %>% 
  filter(!(Att == 0 & DirectlyTreated == 1)) %>% 
        mutate(Pct.MCD = Medicaid / NumberofPatients * 100, 
               Pct.MCR = Medicare / NumberofPatients * 100, 
               Pct.COM = Private / NumberofPatients * 100,
               Pct.None = Uninsured / NumberofPatients * 100 ) %>% 
  select(NumberofPatients, Pct.MCD:Pct.None, Total.Hours, Sites, Mean.Hours, ZipHHI, Perminance, Schedule, Calendar, Tx, DirectlyTreated, ID, Year, Zip, Att, `BHCMIS ID`, UrbanRuralFlag) %>% 
  ### DATA ERRORS
  filter(Total.Hours <= 1344.00)

@@

for (k in 1:9){

  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) #%>% 
  #   inner_join(df.z.temp %>%
  # filter(Year >= 2012) %>%
  # select(ID) %>%
  # group_by(ID) %>%
  # summarise(Counts = n()) %>%
  # filter(Counts == 12), by = c("ID"))

  #%>% filter(Att == 0 | Att > 2010)

  df.z.temp2 <- df.z.temp %>% filter(Year >= 2012) %>% filter(Att %notin% c(2011))

  colnames(df.z.temp2)[k] <- "Outcome"

  # 
  #   outlier.vals <- quantile(df.z.temp2$Outcome, p = c(0.005, 0.995), na.rm = TRUE)
  # df.z.temp2 <- df.z.temp2 %>% 
  #   mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
  #                           ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))

  model <-  did2s(
      data = df.z.temp2, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx * (1 - DirectlyTreated), ref = FALSE)  + I(Tx * DirectlyTreated),
      #second_stage = ~ i(Tx , ref = FALSE)  + I(Tx * DirectlyTreated),
        cluster_var = "ID",
      verbose = TRUE
    )

@@

zip.estimates <- data.frame(cbind(colnames(df.z.temp)[1:9], (coeffs[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(Estimate = round(as.numeric(Estimate), 2), `95% CI` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(`Std..Error`), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(`Std..Error`), 2), sep = "")) %>% 
  mutate(Estimate.1 = round(as.numeric(Estimate.1), 2), `95% CI.1` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(`Std..Error.1`), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(`Std..Error.1`), 2), sep = "")) %>% 
  select(V1, Estimate, `95% CI`, `Pr...t..`, Estimate.1, `95% CI.1`, `Pr...t...1`)

zip.estimates <- zip.estimates[c(9, 1, 6, 2:5, 7:8),]
rownames(zip.estimates) <- NULL

zip.estimates %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Estimate","95% CI","p-value", "Estimate","95% CI", "p-value")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Overall Impacts" = 3, "Patient and Payer Mix" = 4, "Access" = 2)) %>% 
  add_header_above(c(" " = 1, "Directly Competitive" = 3, "Indirectly Competitive" = 3)) %>% 
  add_header_above(c("DID-Estimated Effects of Competitive Shocks on Zip Codes in Incumbent Clinics' Service Area" = 7))
